\documentclass[11pt,courier]{navymemo}

\author{Dennis Evangelista}
\title{Letter of recommendation ICO MIDN 2/C L Davis}
\navysubj{Letter of recommendation ICO MIDN 2/C L Davis}
%\navyfiling{5200.1}
%\navyserial{16-0001}
\date{\today}
%\navymarking{UNCLASSIFIED}

\usepackage{designature}

\begin{document}
\makedateblock{}

\MEMORANDUM{}

\begin{navyletterheader}
\navyfrom{Asst Prof Evangelista}
\navyto{Trident Fellowship Selection Committee}
\navyskip{}%
\navysubjline{}%
\end{navyletterheader}

\section{} 
I am happy to recommend MIDN 2/C Lenny Davis for the Trident Fellowship.  Mr.~Davis is an outstanding midshipman who embodies academic excellence, evidenced by his 3.96 QPR and \#8 OOM, and has high potential for graduate study.  

\section{}
I was Mr.~Davis’ instructor in ES281C Intro to Drone Technology, the quadrotor version of our "School of Drones". In addition, Mr.~Davis is active in the Squad With Autonomous Teammates Challenge (SWAT-C), an ONR-funded effort to examine how autonomy at a squad level can impact Marine Corps operations in a one-block war. As the secretary and drone racing czar for the USNA Student Chapter of the Academy of Model Aeronautics, he has taken an active role in training others in UAS operations. With his experience here at USNA, Mr.~Davis secured an intership at Dam Neck, VA working with NSW on projects relating to UAS. Our goal with School of Drones is to build drone experience early so that midshipmen can reach graduate-level work in autonomy and system design by the time they are upperclass; Mr.~Davis is one of our first midshipmen to fulfill this goal and it has been a delight watching him progress. He is well positioned to be a leader in a future (autonomous) fleet. 

\section{}
Mr.~Davis intends to pursue graduate education and is well situated to do so.  I believe his early drone experiences will also set him up for outstanding work in graduate school. I am excited to see where Mr.~Davis goes with autonomy, robotics, and controls; and I expect him to drive future transformation wherever he ends up in the fleet.

\respectfully{}
\signature{\includesignature}
\signature{D EVANGELISTA}

\end{document}